Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-22 _02_filtering_data.Rmd

```{r add_outlier}
# make a copy
data_copy <- copy(data)

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot()+
  geom_path(data = data_copy,
            aes(x, y),
            col = "grey",
            lwd = 0.2)+
  geom_point(data = data_copy[500:800, ],
             aes(x, y),
             size = 0.2,
             shape = 2, col = pal[4])+
  geom_point(data = data_copy[!data_copy[500:800, ],
                              on = c("x", "y")],
             aes(x, y, 
                 col = (in_speed >= 0.03 & out_speed >= 0.03),
                 shape = (in_speed >= 0.03 & out_speed >= 0.03)),
             show.legend = F,
             alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  scale_color_manual(values = c(pal[3], "black"))+
  scale_shape_manual(values = c(16, 21))+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))
```

@@

```{r echo=FALSE}
# get plots
fig_reflection <-
  ggplot()+
    geom_path(data = reflection,
             aes(x, y),
             alpha = 1,
             col = "grey",
             lwd = 0.2)+
  geom_point(data = reflection,
             aes(x, y),
             alpha = 0.5,
             col = "grey50",
             shape = 16)+
  geom_point(data = data_no_reflection,
             aes(x, y),
             alpha = 0.5,
             colour = pal[3],
             shape = 16,
             show.legend = F)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))

>>>>

```{r add_outlier, eval=FALSE}
# make a copy
data_copy <- copy(data)

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot()+
  geom_path(data = data_copy,
            aes(x, y),
            col = "grey",
            lwd = 0.2)+
  geom_point(data = data_copy[500:800, ],
             aes(x, y),
             size = 0.5,
             shape = 2, col = pal[4])+
  geom_point(data = data_copy[!data_copy[500:800, ],
                              on = c("x", "y")],
             aes(x, y, 
                 col = (in_speed >= 0.03 & out_speed >= 0.03),
                 shape = (in_speed >= 0.03 & out_speed >= 0.03)),
             show.legend = F,
             alpha = 1,
             size = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  scale_color_manual(values = c(pal[3], "black"))+
  scale_shape_manual(values = c(16, 21))+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))
```

@@

```{r echo=FALSE}
# get plots
fig_reflection <-
  ggplot()+
    geom_path(data = reflection,
             aes(x, y),
             alpha = 1,
             col = "grey",
             lwd = 0.2)+
  geom_point(data = reflection,
             aes(x, y),
             alpha = 0.5,
             col = "grey",
             size = 0.5,
             shape = 16)+
  geom_point(data = data_no_reflection,
             aes(x, y),
             # alpha = 0.5,
             size = 0.5,
             colour = pal[3],
             shape = 16,
             show.legend = F)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))
